Analysis of 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-12 introduction.tex
done with introduction, for now. next is the methodology section

In this article we use the visibility graph method to analyze the seismicity of northern Iran for the 2005--2015 period. We focus our analysis the last decade period because previous studies on the analysis of seismic catalogs for the region have shown that this period has the most complete datasets, especially for the case of small earthquakes with $M<4$ \citep[e.g.][]{Khoshnevis2016}. We analyze this region considering three dominant seismic areas: Azerbaijan, Alborz, and Kopeh Dagh.

...

>>>>

In this article we use the visibility graph method to analyze the seismicity of northern Iran for the 2005--2015 period. We focus our analysis on the last decade period because previous studies using seismic catalogs for the region of interest have shown that this period has the most complete datasets, especially for the case of small $M<4$ earthquakes \citep[e.g.][]{Khoshnevis2016}. Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic areas, namely: Azerbaijan, Alborz, and Kopeh Dagh. These are regional areas of considerable ground shaking activity, with average seismic rates varying between about 0.17 and 3.25 events per year \citep[e.g.,][]{Nemati2015}. The considerable amount of earthquakes registered in a 10-year period facilitates the analysis done with the visibility graph approach within what would otherwise be considered a relatively short period of time, and serves as a good case study to test the capabilities of the method. We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2016}. We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-values for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.
